Blame and Coercion: Together Again for the Second Time

### 2019-10-16 paper.tex
plurals
list todos

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
	Gradual Typing is great. Implementing gradually typed with blame tracking 
	and space efficiency is tricky. There exist two technique to do this: 
	coercion and threesome. Coercion is easy to understand, and easy enough to 
	implement, but difficult to reason about formally. Threesome is hard to 
	understand, easy to implement, and easy to reason about formally. We 
	propose hyper-coercion, which is easy to understand, as easy to implement 
	as coercion, and easy to reason about formally.
\end{abstract}

@@

Implementing gradually typed languages naively on top of blame calculus, 
however, suffices sever space leak.
For example, translation to Blame Calculus can wrap some expressions with code 
that performs runtime type-checking (casts), including those expressions at 
tail position. Thus, mutually tail-recursive functions in source language can 
consume unbounded space at runtime. There are more examples of space leaking in 
\citet{herman2010space}.

@@

\citet{siek2009exploring} decorate \citet{herman2010space}'s coercions with 
labels to restore 
blame-tracking. They also propose that there are four blame 
strategies for their coercion:
$ \{Lazy, Eager\} \times \{D, UD\} $. 
Eager strategies detect more potential type errors, 
but blame more programs.
$ D $ and $ UD $ assign blame labels differently.
They prove partially that their \lazyUD{} coercion is correct by showing 
that it simulates the Blame Calculus in \cite{wadler2009well}. It is unknown, 
however, whether the simulation also works in the other direction.

\citet{siek2010threesomes} proposes another approach to combine blame 
tracking and space efficiency. Their solution represents casts with threesomes, 
a novel cast representation.
They show that their calculus bisimulates the \lazyUD{} coercion 
calculus in \citet{siek2009exploring} and the Blame Calculus in 
\citet{wadler2009well}. They also prove that threesome is space-efficient as 
well.

\citet{siek2012interpretations} present the first \lazyD{} Blame Calculus and 
revised coercion calculi.
They simplify the coercion calculi by only 
working with normal coercions (i.e. coercions in normal form). 
They conjecture that their revised coercion calculi bi-simulate the 
corresponding Blame Calculi.

Following \citet{siek2010threesomes}, \citet{garcia2013calculating} develops
threesome for other blame strategies. After studying in depth the relation 
between coercion and threesome,
he claims that normal coercion with labels is easy to understand but hard to 
implement and hard to reason about, and that 
threesome with labels, however, is easy to implement and easy to reason about 
but hard to understand. 
His claim is mostly affirmed by the group of people who develop threesome 
(\citet{siek2015blame}).
His threesome calculi are equivalent to the coercion calculi in 
\citet{siek2009exploring} because the former ones are derived from the latter 
ones.

\citet{siek2015blame} revisit the coercion-based approach. They revise the 
\lazyUD{} coercion in \citet{siek2012interpretations} and prove that 
their revised coercion calculus bi-simulates the \lazyUD{} Blame Calculus.

@@

We prove formally that the \lazyD{} (resp. \lazyUD{}) hyper-coercion calculus 
bi-simulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is 
the first bi-simulation proof for the \lazyD{} Blame Calculus as far as we know.

@@

%One might be tempted to conclude that inconsistency is the root of all runtime 
%type errors (blames). In the setting of gradual typing, however, runtime 
%type-checking is usually gradual as well. 
$ S \smile T $ reads ``$ S $ and $ T $ are shallowly-consistent''. Two types 
are shallowly consistent if one of them is $ \star $, or they have the same 
top-most type constructor. Shallow-inconsistency is the root of all blames in 
all lazy strategies -- casting a value to a shallowly inconsistent type leads 
to a blame. Shallow-consistency is reflexive, symmetric, but 
not transitive.

@@

Let $ o $ ranges over observations. They are what would be observed if a 
program terminates. Observations include all constructors and blames.

@@

	\stxrule{\kappa}{continuations}{
		\mathtt{stop} \mid{}
		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{cons_2} \; v \; \kappa \mid{}
		\mathtt{inl} \; \kappa \mid{}
		\mathtt{inr} \; \kappa
	}
	\stxrulecont{
		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{app_2} \; v \; \kappa \mid{}
		\mathtt{car} \; \kappa \mid{}
		\mathtt{cdr} \; \kappa \mid
		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
	}
	\stxrulecont{	
		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
		\langle c \rangle \kappa
	}
	\end{array}
	\]

@@

	\redrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
			}{(\mathtt{car} \; \kappa)}
	}{
		\sOOreturn{v}{(
			\mathtt{car} \;
			\langle \cOOcast{T_1}{l}{T_3} \rangle \kappa
			)}
	}{}

	\redrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
		}{(\mathtt{cdr} \; \kappa)}
	}{
		\sOOreturn{v}{(
			\mathtt{cdr} \;
			\langle \cOOcast{T_2}{l}{T_4} \rangle \kappa
			)}
	}{}

@@

Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
Calculus in the style of CEK machines (\citet{felleisen1986control}). 
We conjecture that this CEK machines agree with the \lazyD{} blame calculus in 
\citet{siek2012interpretations}.
We will show in \hyperref{sec:hyper-coercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hyper-coercions.

@@

	\comprule{
		\hyperCoercionC{h}{m_1}{t_1}
	}{
		\hyperCoercionC{\epsilon}{m_2}{t_2}
	}{
		\hyperCoercionC{h}{m'}{t'}
	}{
		\sidecond{
			t_1 \neq \bot^{\centerdot} \; \text{and} \;
			m_1 \fatsemi^{\ell} (m_2, t_2) = (m', t')
		}
	}

	\comprule{
		\hyperCoercionC{h}{m_1}{t_1}
	}{
		\hyperCoercionC{?^{l'}}{m_2}{t_2}
	}{
		\hyperCoercionC{h}{m'}{t'}
	}{
		\sidecond{
			t_1 \neq \bot^{\centerdot} \; \text{and} \;
			m_1 \fatsemi^{l'} (m_2, t_2) = (m', t')
		}
	}
	\end{array}
	\]

@@

\lazyD{} HC constructors are in \figref{fig:HC-D}.

$ c_1 \fatsemi^\ell c_2 = c' $ composes two hyper-coercions. The target of $ 
c_1 $ and the source of $ c_2 $ might be different, in which case $ \ell $ must 
be a label.
$ m_1 \fatsemi^\ell (m_2,t) = (m',t') $ composes a middle with a 
pair of a middle and a tail. Similarly, the target of $ m_1 $ and the source of 
$ m_2 $ might be different, in which case $ \ell $ must be a label.
$ seq(c_1,c_2) $ composes two coercions where the target type of $ c_1 $ is 
equal to the source type of $ T_2 $.
$ id(T) $ constructs an identity coercion of $ T $ with the help of $ id(P) $.
$ cast(T_1,l,T_2) $ constructs a coercion from a source type, a label, and a 
target type.

\begin{proposition}[\lazyD\ Hyper-coercions is a Monoid]
	For all $c : T_1 \Longrightarrow T_2$,
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c) = c$,
		\item $seq(c,id(T_2)) = c$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{proposition}

@@

	\stxrule{v}{values}{
		\hcvOOtt \mid
		\hcvOOfun{c_1}{\rho}{x}{b}{c_2} \mid
		\hcvOOcons{v_1}{c_1}{v_2}{c_2}
	}
	\stxrulecont{
		\hcvOOinl{v}{c} \mid
		\hcvOOinr{v}{c} \mid
		\hcvOOinj{P}{v}
	}
	\stxrule{r}{cast results}{
		\rOOsucc{v} \mid
		\rOOfail{l}
	}
	\stxrule{s}{states}{
		\sOOinspect{e}{\rho}{\kappa} \mid{}
		\sOOreturn{v}{\kappa} \mid{}
		\sOOhalt{o}
	}
	\stxrule{\kappa}{continuation}{
		(c,k)
	}
	\stxrule{k}{pre-continuations}{
		\hckOOmt \mid{}
		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{cons_2} \; v \; \kappa \mid{}
		\mathtt{inl} \; \kappa \mid{}
		\mathtt{inr} \; \kappa
	}
	\stxrulecont{
		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{app_2} \; v \; \kappa \mid{}
		\mathtt{car} \; \kappa \mid{}
		\mathtt{cdr} \; \kappa
	}
	\stxrulecont{
		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa \mid
		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa
	}
	\end{array}
	\]

@@

In this section we describe a subset of SR, where all 
elements implement the \lazyD{} blame strategy. We will show in 
Subsection~\ref{sec:LDHC-correct} that the \lazyD\ HC is in this subset.

@@

\subsection{Relating All Surely \lazyD{} Cast Representations}

With the properties of surely \lazyD{} CR, it is straightforward to proof that 
all machines instantiated with these CRs bi-simulate each other. 
The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
derived from the definition of states. We omit subscripts when there is no 
ambiguity. \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
}
\quad
\inference{
	\kappa_1 \approx \kappa_2 &
	v_1 \approx v_2
}{
	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
}
\quad
\inference{
}{
	\sOOhalt{o} \approx \sOOhalt{o}
}
\end{gather*}

\begin{proposition}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
	\label{thm:CEKS-bisim}
	If 
	$ C_1 $ and $ C_2 $ are surely \lazyD,
	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
	$ s_1 \approx s_3 $,
	$ \judgeSreduce{C_1}{s_1}{s_2} $,
	then there exists an $ s_4 $ such that
	\begin{itemize}
	\item $ s_2 \approx s_4 $ and
	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
	\end{itemize}
\end{proposition}
\begin{proof}
	The key ideas of this proof are undoing sequencing with the property (2) of 
	surely \lazyD{} CR, and handling all possibly uses of $ 
	cast(T,l,T) $ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
	\label{thm:surely-lazyD-eqv}
	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
	are surely \lazyD cast representations,
	\[
	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
	e \Downarrow_{S(C_2)} o
	\]
\end{proposition}
\begin{proof}
	Immediately from Proposition~\ref{thm:CEKS-bisim}.
\end{proof}

\subsection{Relating All Surely \lazyD{} Cast Representations to $\mathcal{D}$}

So far, we have related all surely \lazyD{} CRs, i.e. they are equivalent to 
each other. But this does not mean they respect the semantics of the \lazyD{} 
Blame Calculus. We solve prove this part in this subsection.

The state bisimilarity here ($\eqvDS{C}{s}{s}$) is mostly derived from the 
definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
between continuations, between values, and from continuations to 
pre-continuations.

\todo[inline]{bisimilarity}

@@

To show that \lazyD\ HC is correct, we first show it is surely \lazyD, then 
uses the Theorem~\ref{thm:surely-lazyD-correct} to prove its correctness.

@@

\begin{theorem}[\lazyD{} Hyper-coercion Respect $ \mathcal{D} $]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	\judgeDBeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{H}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:hc-surely-lazyD} and 
	Theorem~\ref{thm:surely-lazyD-correct}.
\end{proof}

>>>>

% to-dos
\newcommand{\todoKC}[1]{\todo[inline]{KC needs to #1}}

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
	\todoKC{rewrite abstract}
	Gradual Typing is great. Implementing gradually typed with blame tracking 
	and space efficiency is tricky. There exist two technique to do this: 
	coercion and threesome. Coercion is easy to understand, and easy enough to 
	implement, but difficult to reason about formally. Threesome is hard to 
	understand, easy to implement, and easy to reason about formally. We 
	propose hyper-coercion, which is easy to understand, as easy to implement 
	as coercion, and easy to reason about formally.
\end{abstract}

@@

Implementing gradually typed languages naively on top of blame calculus, 
however, suffices sever space leak.
For example, translation to Blame Calculus can wrap some expressions with code 
that performs runtime type-checking (casts), including expressions at 
tail positions. Thus, mutually tail-recursive functions in source language can 
consume unbounded space at runtime. There are more examples of space leaking in 
\citet{herman2010space}.

@@

\citet{siek2009exploring} decorate \citet{herman2010space}'s coercions with 
labels to restore 
blame-tracking. They also propose that there are four blame 
strategies for their coercion:
$ \{Lazy, Eager\} \times \{D, UD\} $. 
Eager strategies detect more potential type errors, 
but blame more programs.
$ D $ and $ UD $ assign blame labels differently.
They prove their \lazyUD{} coercion simulates the Blame Calculus in 
\cite{wadler2009well}. It is unknown, however, whether the simulation in the 
other direction also works.

\citet{siek2010threesomes} proposes another approach to combine blame 
tracking and space efficiency. Their solution represents casts with threesomes, 
a novel cast representation. Threesome is proved space-efficient as well.
They prove that their calculus bisimulates the \lazyUD{} coercion 
calculus in \citet{siek2009exploring} and the Blame Calculus in 
\citet{wadler2009well}.

\citet{siek2012interpretations} present the first \lazyD{} Blame Calculus and 
revised coercion calculi.
They simplify the coercion calculi by only 
working with normal coercions (i.e. coercions in normal form). 
They conjecture that their revised coercion calculi bisimulate the 
corresponding Blame Calculi.

\citet{garcia2013calculating} develops
threesome for other blame strategies. After studying in depth the connection 
between coercion and threesome,
he claims that normal coercion with labels is easy to understand but hard to 
implement and hard to reason about, and that 
threesome with labels, however, is easy to implement and easy to reason about 
but hard to understand. 
His claim is mostly affirmed by the group of people who develop threesome 
(\citet{siek2015blame}).
His threesome calculi are equivalent to the coercion calculi in 
\citet{siek2009exploring} because the former ones are derived from the latter 
ones.

\citet{siek2015blame} revisit the coercion-based approach. They revise the 
\lazyUD{} coercion in \citet{siek2012interpretations} and prove that 
their revised coercion calculus bisimulates the \lazyUD{} Blame Calculus.

@@

We prove formally that the \lazyD{} (resp. \lazyUD{}) hyper-coercion calculus 
bisimulates the \lazyD{} (resp. \lazyUD{}) Blame Calculus. This is 
the first bi-simulation proof for the \lazyD{} Blame Calculus as far as we know.

@@

%One might be tempted to conclude that inconsistency is the root of all runtime 
%type errors (blames). In the setting of gradual typing, however, runtime 
%type-checking is usually gradual as well. 
$ S \smile T $ reads ``$ S $ and $ T $ are shallowly-consistent''. Two types 
are shallowly consistent if one of them is $ \star $, or they have the same 
type constructor at the top. Shallow-inconsistency is the root of all blames in 
all lazy strategies -- casting a value to a shallowly inconsistent type leads 
to a blame. Shallow-consistency is reflexive, symmetric, but 
not transitive.

@@

Let $ o $ ranges over observations. They are what would be observed if a 
program terminates. Observations include all value constructors and blames.

@@

	\stxrule{\kappa}{continuations}{
		\mathtt{stop} \mid{}
		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{cons_2} \; v \; \kappa \mid{}
		\mathtt{inl} \; \kappa \mid{}
		\mathtt{inr} \; \kappa
	}
	\stxrulecont{
		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{app_2} \; v \; \kappa \mid{}
		\mathtt{fst} \; \kappa \mid{}
		\mathtt{snd} \; \kappa \mid
		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa
	}
	\stxrulecont{	
		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa \mid
		\langle c \rangle \kappa
	}
	\end{array}
	\]

@@

	\redrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
			}{(\mathtt{fst} \; \kappa)}
	}{
		\sOOreturn{v}{(
			\mathtt{fst} \;
			\langle \cOOcast{T_1}{l}{T_3} \rangle \kappa
			)}
	}{}

	\redrule{
		\sOOreturn{
			\vOOcast{v}{\cOOcast{\POOprod{T_1}{T_2}}{l}{
					\POOprod{T_3}{T_4}}}
		}{(\mathtt{snd} \; \kappa)}
	}{
		\sOOreturn{v}{(
			\mathtt{snd} \;
			\langle \cOOcast{T_2}{l}{T_4} \rangle \kappa
			)}
	}{}

@@

Fig.~\ref{machine-cekc} defines the dynamic semantics of the \lazyD{} Blame 
Calculus in the style of CEK machine (\citet{felleisen1986control}). 
We conjecture that this CEK machine agree with the \lazyD{} blame calculus in 
\citet{siek2012interpretations}.
We will show in Section~\ref{sec:hyper-coercion} that this abstract machine is 
equivalent to an abstract machine that represents casts with hyper-coercions.

\todoKC{change the reduction rules of case}

@@

	\comprule{
		\hyperCoercionC{h}{m_1}{t_1}
	}{
		\hyperCoercionC{\epsilon}{m_2}{t_2}
	}{
		\hyperCoercionC{h}{m'}{t'}
	}{
		\sidecond{
			m_1 \fatsemi^{\ell} (m_2, t_2) = (m', t')
			 \; \text{and} \;
			 \forall l. t \neq \bot^{l}
		}
	}

	\comprule{
		\hyperCoercionC{h}{m_1}{t_1}
	}{
		\hyperCoercionC{?^{l'}}{m_2}{t_2}
	}{
		\hyperCoercionC{h}{m'}{t'}
	}{
		\sidecond{
			m_1 \fatsemi^{l'} (m_2, t_2) = (m', t')
			\; \text{and} \;
			\forall l. t \neq \bot^{l} 
		}
	}
	\end{array}
	\]

@@

\figref{fig:HC-D} defines the constructors of \lazyD{} HC.

\todoKC{check consistency before using middle composition.}

$ c_1 \fatsemi^\ell c_2 = c' $ composes two HCs. The target of $ 
c_1 $ and the source of $ c_2 $ might be different, in which case $ \ell $ must 
be a label.
$ m_1 \fatsemi^\ell (m_2,t) = (m',t') $ composes a middle with a 
pair of a middle and a tail. Similarly, the target of $ m_1 $ and the source of 
$ m_2 $ might be different, in which case $ \ell $ must be a label.
$ seq(c_1,c_2) $ composes two coercions where the target type of $ c_1 $ is 
equal to the source type of $ T_2 $.
$ id(T) $ constructs an identity coercion of $ T $ with the help of $ id(P) $.
$ cast(T_1,l,T_2) $ constructs a coercion from a source type, a label, and a 
target type.

\begin{proposition}[\lazyD\ Hyper-coercions is a Monoid]
	\label{thm:hc-monoid}
	For all $c : T_1 \Longrightarrow T_2$,
	$c_1 : T_1 \Longrightarrow T_2$,
	$c_2 : T_2 \Longrightarrow T_3$, and
	$c_3 : T_3 \Longrightarrow T_4$,
	\begin{enumerate}
		\item $seq(id(T_1),c) = c$,
		\item $seq(c,id(T_2)) = c$, and
		\item $seq(seq(c_1, c_2), c_3) = seq(c_1, seq(c_2, c_3))$.
	\end{enumerate}
\end{proposition}

@@

	\stxrule{v}{values}{
		\hcvOOtt \mid
		\hcvOOfun{c_1}{\rho}{x}{b}{c_2} \mid
		\hcvOOcons{v_1}{c_1}{v_2}{c_2}
	}
	\stxrulecont{
		\hcvOOinl{v}{c} \mid
		\hcvOOinr{v}{c} \mid
		\hcvOOinj{P}{v}
	}
	\stxrule{r}{cast results}{
		\rOOsucc{v} \mid
		\rOOfail{l}
	}
	\stxrule{s}{states}{
		\sOOinspect{e}{\rho}{\kappa} \mid{}
		\sOOreturn{v}{\kappa} \mid{}
		\sOOhalt{o}
	}
	\stxrule{\kappa}{continuation}{
		(c,k)
	}
	\stxrule{k}{pre-continuations}{
		\hckOOmt \mid{}
		\mathtt{cons_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{cons_2} \; v \; \kappa \mid{}
		\mathtt{inl} \; \kappa \mid{}
		\mathtt{inr} \; \kappa
	}
	\stxrulecont{
		\mathtt{app_1} \; e \; \rho \; \kappa \mid{}
		\mathtt{app_2} \; v \; \kappa \mid{}
		\mathtt{fst} \; \kappa \mid{}
		\mathtt{snd} \; \kappa
	}
	\stxrulecont{
		\mathtt{case_1} \; e_1 \; e_2 \; \rho \; \kappa \mid
		\mathtt{case_2} \; v   \; e   \; \rho \; \kappa \mid{}
		\mathtt{case_3} \; v_1 \; v_2 \; \rho \; \kappa
	}
	\end{array}
	\]

@@

In this section we describe a subset of cast representations, where all 
elements implement the \lazyD{} blame strategy. We will show in 
Subsection~\ref{sec:LDHC-correct} that the \lazyD\ HC is in this subset.

@@

\subsection{All Surely \lazyD{} and Monoidic Cast Representations Respect 
$\mathcal{D}$}

We use bisimulation to proof equivalence between the two machines.
The state bisimilarity ($\eqvDS{C}{s}{s}$) is mostly derived from the 
definitions of $ \mathcal{D} $. Exceptions include the bisimilarity relations 
between continuations, between values, and from continuations to 
pre-continuations. We omit subscripts when there is no ambiguity.

\todoKC{write down the exceptional bisimilarity relations}

@@

@@

\begin{theorem}[\lazyD{} Hyper-coercion Respect $ \mathcal{D} $]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $ 
	\[
	\judgeDBeval{e}{o} \; \text{if and only if} \; 
	\judgeSeval{H}{e}{o}
	\]
\end{theorem}
\begin{proof}
	Immediately from Lemma~\ref{thm:surely-monoidic-eval},
	Lemma~\ref{thm:hc-surely-lazyD}, and 
	Proposition~\ref{thm:hc-monoid}.
\end{proof}

\subsection{Extra Theorems}

In these section we show some extra theorems that might be useful in proving 
the correctness of other cast representations.

With the properties of surely \lazyD{} CR, it is straightforward to proof that 
all machines instantiated with these CRs bisimulate each other. 
The state bisimilarity ($\eqvS{C}{C}{s}{s}$) is 
derived from the definition of states. We omit subscripts when there is no 
ambiguity. \begin{gather*}
\inference{
	\rho_1 \approx \rho_2 &
	\kappa_1 \approx \kappa_2
}{
	\sOOinspect{e}{\rho_1}{\kappa_1} \approx \sOOinspect{e}{\rho_2}{\kappa_2}
}
\quad
\inference{
	\kappa_1 \approx \kappa_2 &
	v_1 \approx v_2
}{
	\sOOreturn{v_1}{\kappa_1} \approx \sOOreturn{v_2}{\kappa_2}
}
\quad
\inference{
}{
	\sOOhalt{o} \approx \sOOhalt{o}
}
\end{gather*}

\begin{lemma}[Strong Bi-simulation among $ \mathcal{S}(\cdot) $]
	\label{thm:CEKS-bisim}
	If 
	$ C_1 $ and $ C_2 $ are surely \lazyD,
	$ s_1, s_2 \in S(C_1) $ and $ s_3 \in S(C_2) $,
	$ s_1 \approx s_3 $,
	$ \judgeSreduce{C_1}{s_1}{s_2} $,
	then there exists an $ s_4 $ such that
	\begin{itemize}
	\item $ s_2 \approx s_4 $ and
	\item $ s_3 \longrightarrow_{S(C_2)} s_4 $
	\end{itemize}
\end{lemma}
\begin{proof}
	The key ideas of this proof are undoing sequencing with the property (2) of 
	surely \lazyD{} CR, and handling all possibly uses of $ 
	cast(T,l,T) $ with property (3)-(11).
\end{proof}

\begin{proposition}[Equivalence of Surely \lazyD{} Cast Representations]
	\label{thm:surely-lazyD-eqv}
	If $ \judgetype{\emptyset}{e}{T} $, $ o : T $, and $ C_1 $ and $ C_2 $ 
	are surely \lazyD\ cast representations,
	\[
	e \Downarrow_{S(C_1)} o \; \text{if and only if} \; 
	e \Downarrow_{S(C_2)} o
	\]
\end{proposition}
\begin{proof}
	Immediately from Lemma~\ref{thm:CEKS-bisim}.
\end{proof}
